---
title: "Testing COPE"
author: "Alexandros Rekkas"
date: "`r Sys.Date()`"
output:
  bookdown::pdf_document2:
    number_sections: yes
    toc: yes
  bookdown::html_document2:
    number_sections: yes
    toc: yes
---

```{r, eval=TRUE, echo=FALSE, message=FALSE}
library(dplyr)
source("../R/Calculations.R")
source("../R/Plotting.R")
```


# Testing supporting functions

This set of tests evaluates the functions used to support the server function. These functions are used for calculating relevant quantities, e.g. 28-day mortality risk.

Function `createModelMatrix` creates the model matrix based on a set of covariates and a list of transformations.

```{r}
testthat::test_that(
	"Creation of model matrix works",
	{
		testthat::expect_equal(
			createModelMatrix(
				covariates      = rep(1, 6),
				transformations = transformationsMortality
			),
			c(1, rep(0, 5))
		)
	}
)
```

Function `createLinearPredictor` calculates the linear predictor of a prediction based on a provided model matrix, a vector of $\beta$ coefficients and an intercept

```{r}
testthat::test_that(
	"Creation of linear predictor works",
	{
		testthat::expect_equal(
			createLinearPredictor(
				modelMatrix = rep(1, 6),
				beta        = rep(1, 6),
				intercept   = 1
			),
			matrix(7)
		)
	}
)
```


Function `logisticProbability` calculates the logistic probability (%) based on a provided linear predictor value.

```{r}
testthat::test_that(
	"Logistic probability calculation from linear predictor works",
	{
		testthat::expect_equal(
			logisticProbability(0),
			50
		)
	}
)
```


Finally, function `extractQuantiles` extracts the required quantiles for the calibration plot, based on the stored dataframe of `calibrationQuantiles`, the outcome of interest and the hospital under consideration.

```{r}
testthat::test_that(
	"Extraction of calibration quantiles works",
	{
		testthat::expect_equal(
			extractQuantiles(
				outcome              = 1,
				center               = 1,
				calibrationQuantiles = data.frame(
					center  = 1,
					outcome = 1,
					quant20 = 20,
					quant40 = 40,
					quant60 = 60,
					quant80 = 80
				)
			),
			c(
				quant20 = 20, quant40 = 40,
				quant60 = 60, quant80 = 80
			)
		)
	}
)
```


# Testing server functions

Here we perform a set of unit tests to ensure that server-side operations work the way they should. We start by looking at calculations tasks run within the server function.

First, the `currentInputData` reactive dataframe should contain all the provided inputs.


```{r}
shiny::testServer(
	expr = {
		session$setInputs(
			age                       = 70,
			respiratoryRate           = 19,
			ldh                       = 244,
			crp                       = 48,
			albumin                   = 39,
			urea                      = 6.5,
			calculatePredictionButton = "click"
		)
		
		testthat::test_that(
			"The reactive input dataframe is correct",
			{
				testthat::expect_equal(
					currentInputData(),
					data.frame(
						age             = 70,
						respiratoryRate = 19,
						crp             = 48,
						ldh             = 244,
						albumin         = 39,
						urea            = 6.5
					)
				)
			}
		)
		
		session$setInputs(
			age                       = 70,
			respiratoryRate           = 19,
			ldh                       = 2440,
			crp                       = 48,
			albumin                   = 39,
			urea                      = 6.5,
			calculatePredictionButton = "click"
		)
		
		testthat::test_that(
			"The reactive input dataframe is updated",
			{
				testthat::expect_equal(
					currentInputData(),
					data.frame(
						age             = 70,
						respiratoryRate = 19,
						crp             = 48,
						ldh             = 2440,
						albumin         = 39,
						urea            = 6.5
					)
				)
			}
		)
		
	}
)

```

