---
title: "Testing COPE"
author: "Alexandros Rekkas"
date: "`r Sys.Date()`"
output:
  bookdown::pdf_document2:
    number_sections: yes
    toc: yes
  bookdown::html_document2:
    number_sections: yes
    toc: yes
---

```{r, eval=TRUE, echo=FALSE, message=FALSE}
library(dplyr)
source("../R/Calculations.R")
source("../R/Plotting.R")
```


# Testing supporting functions

This set of tests evaluates the functions used to support the server function. These functions are used for calculating relevant quantities, e.g. 28-day mortality risk.

Function `createModelMatrix` creates the model matrix based on a set of covariates and a list of transformations.

```{r}
testthat::test_that(
	"Creation of model matrix works",
	{
		testthat::expect_equal(
			createModelMatrix(
				covariates      = rep(1, 6),
				transformations = transformationsMortality
			),
			c(1, rep(0, 5))
		)
	}
)
```

Function `createLinearPredictor` calculates the linear predictor of a prediction based on a provided model matrix, a vector of $\beta$ coefficients and an intercept

```{r}
testthat::test_that(
	"Creation of linear predictor works",
	{
		testthat::expect_equal(
			createLinearPredictor(
				modelMatrix = rep(1, 6),
				beta        = rep(1, 6),
				intercept   = 1
			),
			matrix(7)
		)
	}
)
```


Function `logisticProbability` calculates the logistic probability (%) based on a provided linear predictor value.

```{r}
testthat::test_that(
	"Logistic probability calculation from linear predictor works",
	{
		testthat::expect_equal(
			logisticProbability(0),
			50
		)
	}
)
```


Finally, function `extractQuantiles` extracts the required quantiles for the calibration plot, based on the stored dataframe of `calibrationQuantiles`, the outcome of interest and the hospital under consideration.

```{r}
testthat::test_that(
	"Extraction of calibration quantiles works",
	{
		testthat::expect_equal(
			extractQuantiles(
				outcome              = 1,
				center               = 1,
				calibrationQuantiles = data.frame(
					center  = 1,
					outcome = 1,
					quant20 = 20,
					quant40 = 40,
					quant60 = 60,
					quant80 = 80
				)
			),
			c(
				quant20 = 20, quant40 = 40,
				quant60 = 60, quant80 = 80
			)
		)
	}
)
```


# Testing server functions

Here we perform a set of unit tests to ensure that server-side operations work the way they should. We start by looking at calculations tasks run within the server function.

## Interactivity
Interactive values, are server-side variables that depend on the input and, therefore, need to be updated whenever the user alters their selection.

First, the `currentInputData` reactive dataframe should contain all the provided inputs and should update accordingly, when these are changed.


```{r}
shiny::testServer(
	expr = {
		session$setInputs(
			age                       = 70,
			respiratoryRate           = 19,
			ldh                       = 244,
			crp                       = 48,
			albumin                   = 39,
			urea                      = 6.5,
			calculatePredictionButton = "click"
		)
		
		testthat::test_that(
			"The reactive input dataframe is correct",
			{
				testthat::expect_equal(
					currentInputData(),
					data.frame(
						age             = 70,
						respiratoryRate = 19,
						crp             = 48,
						ldh             = 244,
						albumin         = 39,
						urea            = 6.5
					)
				)
			}
		)
		
		session$setInputs(
			age                       = 70,
			respiratoryRate           = 19,
			ldh                       = 2440,
			crp                       = 48,
			albumin                   = 39,
			urea                      = 6.5,
			calculatePredictionButton = "click"
		)
		
		testthat::test_that(
			"The reactive input dataframe is updated",
			{
				testthat::expect_equal(
					currentInputData(),
					data.frame(
						age             = 70,
						respiratoryRate = 19,
						crp             = 48,
						ldh             = 2440,
						albumin         = 39,
						urea            = 6.5
					)
				)
			}
		)
		
	}
)

```

Next, we do the same for the variables that keep track of the current prediction and its placement, relevant to the overall predicted risk fifths, for both outcomes (mortality and ICU admission).The first set of tests evaluates if the initial input is handled appropriately and the second set evaluates if the values are updated correctly.

```{r}
shiny::testServer(
	expr = {
		session$setInputs(
			age                       = 70,
			respiratoryRate           = 19,
			ldh                       = 244,
			crp                       = 48,
			albumin                   = 39,
			urea                      = 6.5,
			calculatePredictionButton = "click"
		)
		
		# Is the prediction for the starting values correct?
		testthat::test_that(
			"Is the prediction for the starting values correct?",
			testthat::expect_equal(
				currentPrediction(),
				list(
					mortality = 4.8,
					icu       = 13.3
				)
			)
		)
		
		# Is the predicted mortality risk assigned to the correct stratum of risk?
		testthat::expect_equal(
			riskFifthMortality(),
			4
		)
		
		# Is the predicted ICU risk assigned to the correct stratum of risk?
		testthat::expect_equal(
			riskFifthIcu(),
			4
		)
		
		
		session$setInputs(
			age                       = 60,
			respiratoryRate           = 30,
			ldh                       = 400,
			crp                       = 100,
			albumin                   = 50,
			urea                      = 10,
			calculatePredictionButton = "click"
		)
		
		testthat::test_that(
			"Current prediction is updated",
			testthat::expect_equal(
				currentPrediction(),
				list(
					mortality = 10.8,
					icu       = 20.6
				)
			)
		)
	}
)

```